P2P-LLM: Collaborative LLM Inference

### 2025-05-05 docs/paper/main.tex
complete

\usepackage{lastpage}
\jmlrheading{23}{2022}{1}{1/21}{9/22}{21-0000}{Author One and Author Two}

@@

\begin{figure}
	\centering
	\begin{tikzpicture}
		\begin{axis}[
				width=12cm,
				height=8cm,
				xlabel={Computational Cost},
				ylabel={Price},
				xlabel style={font=\large},
				ylabel style={font=\large},
				xmin=0, xmax=10,
				ymin=0, ymax=10,
				xtick={0,2,4,6,8,10},
				ytick={0,2,4,6,8,10},
				grid=both,
				title={Pareto Frontier: Computational Cost vs. Price},
				legend pos=north east,
				legend style={font=\footnotesize}
			]

@@

\begin{figure}
	\centering
	\begin{tikzpicture}
		\begin{axis}[
				width=14cm,
				height=8cm,
				xlabel={$p_i$},
				ylabel={Expected Revenue $R(p_i)$},
				domain=0:12,
				samples=200,
				legend pos=north east,
				grid=major,
				thick,
				every axis plot/.append style={very thick},
				title={Expected Revenue Function $R(p_i)$}
			]

@@

@@

\subsection{Simulation Framework}
The simulation framework implements a discrete event-based model of the P2P-LLM network, where each event corresponds to a peer action such as joining the network, processing requests, updating prices, or switching layers. The simulation progresses in timesteps, with each timestep representing a fixed duration (e.g., 1 second in simulated time). At each timestep, the following operations are performed:
\begin{enumerate}
	\item Process pending inference requests through the network
	\item Update node prices according to the gradient ascent algorithm (Equation \ref{eq:optim_price})
	\item Periodically, reallocate nodes to new layers (Equation \ref{eq:max})
	\item Create new contracts for peers without a pending contract
	\item Record metrics for analysis
\end{enumerate}
The simulation parameters can be configured to model various network sizes, LLM architectures, and peer behaviors, allowing for comprehensive sensitivity analysis.

@@

\begin{table}[t]
	\centering
	\caption{P2P-LLM Network Metrics at Different Iteration Steps (Model with 4 Layers, 200 Peers)}
	\label{tab:network-metrics}
	\begin{tabular}{ccccccc}
		\toprule
		\textbf{Iteration} & \textbf{Metric} & \textbf{Layer 1} & \textbf{Layer 2} & \textbf{Layer 3} & \textbf{Layer 4} \\
		\midrule
		\multirow{3}{*}{0}
		                   & Nodes           & 78               & 52               & 34               & 36               \\
		                   & Avg. Price      & 5.42             & 5.28             & 5.87             & 5.31             \\
		\midrule
		\multirow{3}{*}{100}
		                   & Nodes           & 62               & 48               & 43               & 47               \\
		                   & Avg. Price      & 5.89             & 5.96             & 5.72             & 5.68             \\
		\midrule
		\multirow{3}{*}{500}
		                   & Nodes           & 53               & 49               & 50               & 48               \\
		                   & Avg. Price      & 6.12             & 6.08             & 6.10             & 6.05             \\
		\midrule
		\multirow{3}{*}{1000}
		                   & Nodes           & 50               & 50               & 50               & 50               \\
		                   & Avg. Price      & 6.14             & 6.15             & 6.13             & 6.15             \\
		\midrule
		\multirow{3}{*}{5000}
		                   & Nodes           & 50               & 50               & 50               & 50               \\
		                   & Avg. Price      & 6.13             & 6.14             & 6.14             & 6.13             \\
		\bottomrule
	\end{tabular}
\end{table}

>>>>

\usepackage{lastpage}
%\jmlrheading{23}{2022}{1}{1/21}{9/22}{21-0000}{Author One and Author Two}

@@

\begin{figure}[ht]
	\centering
	\begin{tikzpicture}
		\begin{axis}[
				width=10cm,
				height=6cm,
				xlabel={Computational Cost},
				ylabel={Price},
				xlabel style={font=\large},
				ylabel style={font=\large},
				xmin=0, xmax=10,
				ymin=0, ymax=10,
				xtick={0,2,4,6,8,10},
				ytick={0,2,4,6,8,10},
				grid=both,
				title={Pareto Frontier: Computational Cost vs. Price},
				legend pos=north east,
				legend style={font=\footnotesize}
			]

@@

@@

\begin{figure}[h]
	\centering
	\begin{tikzpicture}
		\begin{axis}[
				width=10cm,
				height=6cm,
				xlabel={$p_i$},
				ylabel={Expected Revenue $R(p_i)$},
				domain=0:12,
				samples=200,
				legend pos=north east,
				grid=major,
				thick,
				every axis plot/.append style={very thick},
				title={Expected Revenue Function $R(p_i)$}
			]

@@

\subsection{Simulation Framework}
The simulation framework implements a discrete event-based model of the P2P-LLM network, where each event corresponds to a peer action such as joining the network, processing requests, updating prices, or switching layers. The simulation progresses in timesteps, with each timestep representing a fixed duration (e.g., 1 second in simulated time). At each timestep, the following operations are performed:
\begin{enumerate}
	\item Process pending inference requests through the network
	\item Update node prices according to the gradient ascent algorithm (Equation \ref{eq:optim_price})
	\item Periodically, reallocate nodes to new layers (Equation \ref{eq:max})
	\item Create new contracts for peers without a pending contract
\end{enumerate}
The simulation parameters can be configured to model various network sizes, LLM architectures, and peer behaviors, allowing for comprehensive sensitivity analysis.

@@

\begin{table}[h]
	\centering
	\caption{P2P-LLM Network Metrics at Different Iteration Steps (Model with 4 Layers, 28 Peers)}
	\label{tab:network-metrics}
	\begin{tabular}{ccccccc}
		\toprule
		\textbf{Iteration} & \textbf{Metric} & \textbf{Layer 1} & \textbf{Layer 2} & \textbf{Layer 3} & \textbf{Layer 4} \\
		\midrule
		\multirow{3}{*}{0}
		                   & Nodes           & 10               & 4                & 10               & 4                \\
		                   & Avg. Price      & 1                & 1                & 1                & 1                \\
		\midrule
		\multirow{3}{*}{100}
		                   & Nodes           & 7                & 6                & 10               & 5                \\
		                   & Avg. Price      & 1.92             & 2.20             & 1.80             & 2.31             \\
		\midrule
		\multirow{3}{*}{500}
		                   & Nodes           & 7                & 6                & 8                & 7                \\
		                   & Avg. Price      & 2.33             & 2.40             & 2.29             & 2.33             \\
		\midrule
		\multirow{3}{*}{1000}
		                   & Nodes           & 7                & 7                & 7                & 7                \\
		                   & Avg. Price      & 2.33             & 2.34             & 2.33             & 2.33             \\
		\bottomrule
	\end{tabular}
\end{table}

When running the simulated environment, the behavior of the peers aligns with what is expected based on the theory described above.
The starting state of the network has uniform pricing across all nodes, and there is a high concentration of peers in the first and third layers of the LLM.
As the network progresses toward a state of equilibirum, the prices are expected to rise to meet the demand of the network, and reach a maximum where the expected revenue for the reective node is highest.
Nodes are also expected to change the layer of the LLM they serve based on the location of other nodes in the network. Ideally, the nodes will be evenly distriubted between layers in the network.
Looking at Table \ref{tab:network-metrics}, the expected actions occurs as the iteration of the simulation increases.
It eventually reached a point of equilibrium where the prices and layers are constant.
